### 2023-05-24 manuscript.tex
Update otolith view and export [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/0ae560e58ee5d82015d11abc2962e5875d2d41fe.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/0ae560e58ee5d82015d11abc2962e5875d2d41fe/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5066077464

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...e1e2ef76a476174a4115937d77457037ddec95df}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/e1e2ef76a476174a4115937d77457037ddec95df}{habi/EAWAG-manuscript@e1e2ef7}
on April 24, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 24 Apr 2023{]}. Available: \url{https://osf.io/ecmz4/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{OpenSCAD. {[}cited 24 Apr 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ZjgrPHTa}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{Haberthür D. Jupyter notebooks for image processing and data analysis of EAWAG Cichlids project. 2023. Available: \url{https://github.com/habi/EAWAG/blob/e5d6be6b416b7c66eaf72a563b0ce5648569f54d/rsync-fishes.sh}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0ae560e58ee5d82015d11abc2962e5875d2d41fe}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/0ae560e58ee5d82015d11abc2962e5875d2d41fe/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/0ae560e58ee5d82015d11abc2962e5875d2d41fe}{habi/EAWAG-manuscript@0ae560e}
on May 24, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 24 May 2023{]}. Available: \url{https://osf.io/ecmz4/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{OpenSCAD. {[}cited 24 May 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ZjgrPHTa}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{Haberthür D. Jupyter notebooks for image processing and data analysis of EAWAG Cichlids project. 2023. Available: \url{https://github.com/habi/EAWAG/blob/48197e8f6e7add0d3610ea1b2820f29c9a536bdf/rsync-fishes.sh}}
